\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\usepackage{array}
\usepackage{booktabs}
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{Brief Article}
\author{The Author}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}
At present stage, the size of training data set of Dota and LoL have relatively 56082 and 15608 lines. We use the presence of hero in each match as features, that is 108 number of features. If the hero is at team `Dire', then the value is 1, or the value is -1. In LoL, respectively there are 121 features. 

We applied three machine learning model to approach this problem: Logistic Regression, Neural Networks and Support Vector Machine. In Logistic Regression, We select a learning rate of $\alpha = 0.001$, where the proportion of test set is 30\%, which is randomly picked from the dataset. This approach is simple and easy to implement, but this model has some drawbacks that might lead to invalidity of prediction. In Neural Networks model, we choose to use 3 layers: 1 hidden layer with 100 nodes. The input layer has 108 nodes and the output layer has 2 nodes. We implemented feedforward back propagation neural network. Sigmoid transform was applied and lambda in cost function was set to 0.5. 

We could see that Neural Networks has better result on LoL than Dota, this might because that the game LoL focus more on synergy of heroes. That is to say, the selection of hero in the first stage will have more influence on the result of the match.

\begin{table}[h]
\begin{tabular}{c c c c c}
\hline
\toprule
                       & \multicolumn{2}{c}{LoL}    & \multicolumn{2}{c}{Dota}   \\ 
\midrule
                       & Training Accuracy (\%) & Test Accuracy & Training Accuracy & Test Accuracy \\ \hline
Logistic Regression    & 62.55         & 60.62     & 63.06         & 64.48     \\ \hline
Neural Networks        & 72.63        & 70.77     & 65.12        &64.81     \\ \hline
Support Vector Machine &                &            &                &            \\ 
\bottomrule
\end{tabular}
\end{table}

\end{document}  